---
title: "Group members"
pagetitle: "People - Xing Lab @ East China Normal University"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
# dingliang.jpg: 903 x 778 pixels --> X 25% --> 194.5 pixels height 
# person-icon: 300*300 --> 778*.25/300 = .65
```

<div class="row">
<div class="col-md-4" align="center">

![**[Dingliang Xing](index.html), PI**](dingliang2.jpg){#id .class width=85% height=85%}
</div>
</div>

<div class="row">
<div class="col-md-4" align="center">

![**[Ruyun Zhang](people.html), PhD student**](ruyun.jpg){#id .class width=85% height=85%}

</div>
<div class="col-md-4" align="center">

![**[Jingyue Huang](people.html), Master student**](jingyue.jpg){#id .class width=85% height=85%}

</div>
<div class="col-md-4" align="center">

![**[Yongchao Liu](people.html), Master student**](yongchao.jpg){#id .class width=80% height=80%}

</div>
</div>

<div class="row">
<div class="col-md-4" align="center">


![**[You?](mailto:xingdingliang@gmail.com)**](person-icon.png){#id .class width=195px height=195px} 

</div>
</div>



